Paper 1: Vitis

### 2018-02-14 Paper-1-Vitis.Rmd
Commit from RStudio

```{r}
r_ln <- read_excel("R_DiLP_Vitis_all_added.xlsx", sheet = "riparia.all.ln")
r_ln_mat <- data.matrix(r_ln, rownames.force = NA)
r_ln_fixed <- r_ln_mat[,-(1:3)]
r_ln_fixed[r_ln_fixed == 0] <- NA
#pca_r_all <- pca(r_ln_fixed, method = "nipals", center = TRUE, nPcs = 5)
bpca_r_ll <- pca(r_ln_fixed, method = "bpca", nPcs = 5)
summary(bpca_r_ll)
loadings(bpca_r_ll)
#summary(pca_r_all)
#loadings(pca_r_all)
print(bpca_r_ll)
#print(pca_r_all)
#slplot(pca_r_all)
beep(sound = 3, expr = NULL)
```

@@

```{r}
ac_glm <- glm(leaf~total.teeth, data = ac_all, family = gaussian())
summary(ac_glm)
plot(ac_glm)
```

>>>>

```{r}
r_ln <- read_excel("R_DiLP_Vitis_all_added.xlsx", sheet = "riparia.all.ln")
r_ln_mat <- data.matrix(r_ln, rownames.force = NA)
r_ln_fixed <- r_ln_mat[,-(1:3)]
r_ln_fixed[r_ln_fixed == 0] <- NA
#pca_r_all <- pca(r_ln_fixed, method = "nipals", center = TRUE, nPcs = 5)
bpca_r_ll <- pca(r_ln_fixed, method = "bpca", nPcs = 5)
summary(bpca_r_ll)
loadings(bpca_r_ll)
#summary(pca_r_all)
#loadings(pca_r_all)
print(bpca_r_ll)
#print(pca_r_all)
#slplot(pca_r_all)
```

@@

We ran a GLM for leaf number and total teeth.

```{r}
skim(ac_all)
ac_tt_glm <- glm(leaf~total.teeth, data = ac_all, family = gaussian())
summary(ac_tt_glm)
plot(ac_tt_glm)
```

We ran a GLM for leaf number and feret diameter ratio.

```{r}
ac_fdr_glm <- glm(leaf~feret.diameter.ratio, data = ac_all, family = gaussian())
summary(ac_fdr_glm)
plot(ac_fdr_glm)
```

We ran a GLM for leaf number and tooth area:perimeter.

```{r}
ac_tap_glm <- glm(leaf~tooth.area.perimeter, data = ac_all, family = gaussian())
summary(ac_tap_glm)
plot(ac_tap_glm)
```

We ran a GLM for leaf number and tooth area:internal perimeter.

```{r}
ac_taip_glm <- glm(leaf~tooth.area.int.perimeter, data = ac_all, family = gaussian())
summary(ac_taip_glm)
plot(ac_taip_glm)
```

We ran a GLM for leaf number and average tooth area.

```{r}
ac_ata_glm <- glm(leaf~average.tooth.area, data = ac_all, family = gaussian())
summary(ac_ata_glm)
plot(ac_ata_glm)
```

We ran a GLM for leaf number and tooth area:blade area..

```{r}
ac_taba_glm <- glm(leaf~tooth.area.blade.area, data = ac_all, family = gaussian())
summary(ac_taba_glm)
plot(ac_taba_glm)
```

We ran a GLM for leaf number and teeth:perimeter.

```{r}
ac_tp_glm <- glm(leaf~teeth.perimeter, data = ac_all, family = gaussian())
summary(ac_tp_glm)
plot(ac_tp_glm)
```

We ran a GLM for leaf number and teeth:internal perimeter.

```{r}
ac_tip_glm <- glm(leaf~teeth.int.perimeter, data = ac_all, family = gaussian())
summary(ac_tip_glm)
plot(ac_tip_glm)
```

We ran a GLM for leaf number and perimeter:area.

```{r}
ac_pa_glm <- glm(leaf~perimeter.area, data = ac_all, family = gaussian())
summary(ac_pa_glm)
plot(ac_pa_glm)
```

We ran a GLM for leaf number and perimeter ratio.

```{r}
ac_pr_glm <- glm(leaf~perimeter.ratio, data = ac_all, family = gaussian())
summary(ac_pr_glm)
plot(ac_pr_glm)
```

We ran a GLM for leaf number and compactness.

```{r}
ac_cp_glm <- glm(leaf~compactness, data = ac_all, family = gaussian())
summary(ac_cp_glm)
plot(ac_cp_glm)
```

We ran a GLM for leaf number and shape factor.

```{r}
ac_sf_glm <- glm(leaf~shape.factor, data = ac_all, family = gaussian())
summary(ac_sf_glm)
plot(ac_sf_glm)
```

We ran a GLM for leaf number and teeth:blade area.

```{r}
ac_tba_glm <- glm(leaf~teeth.blade.area, data = ac_all, family = gaussian())
summary(ac_tba_glm)
plot(ac_tba_glm)
beep(sound = 3, expr = NULL)
```

We ran a GLM for leaf number and multiple variables. 
```{r}
ac_clim_glm <- glm(leaf~feret.diameter.ratio + tooth.area.blade.area + teeth.blade.area + teeth.int.perimeter, data = ac_all, family = gaussian())
summary(ac_clim_glm)
plot(ac_clim_glm)
```
